% publications/papers/experimental_predictions.tex

\documentclass[11pt]{article}
\usepackage{amsmath,amsfonts,amssymb,amsthm}
\usepackage{geometry}
\usepackage{authblk}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{bm}
\usepackage{enumitem}

\geometry{margin=1in}
\title{\textbf{Experimental Predictions of the Cross-Absolute Interaction Model}}

\author[1]{Ricardo Jorge Do Vale}
\author[1]{RJV Technologies Ltd}
\date{March 2025}

\begin{document}
\maketitle

\begin{abstract}
This paper derives the experimental predictions of the Enhanced Mathematical Ontology of Absolute Nothingness, with a focus on observable deviations from the Standard Model and General Relativity. It defines specific force signatures, quantum resonances, and curvature anomalies arising from cross-absolute interactions, and provides concrete test conditions using particle accelerators, gravitational interferometry, and vacuum energy detectors. These predictions are not only falsifiable but computable via the AxAbsEnt execution engine, making them suitable for direct simulation and experimental validation.
\end{abstract}

\tableofcontents

\newpage

\section{Overview}

The Enhanced Mathematical Ontology of Absolute Nothingness predicts the emergence of all physical phenomena from cross-absolute interactions between orthogonal irreducible entities. When these interactions manifest in transfinite mediator spaces, they produce quantifiable signatures detectable under controlled physical conditions.

This document formalizes the testable outcomes of the theory in four domains:

\begin{enumerate}[label=\textbf{P\arabic*}]
    \item Anomalous force distributions and unification deviations
    \item Resonance artifacts in vacuum-fluctuation-sensitive environments
    \item Cosmological-scale deviations in curvature entropy flux
    \item Non-linear information transfer events not explainable by entanglement
\end{enumerate}

\section{Prediction P1: Force Signature Deviations}

\subsection{Test Protocol}

Standard Model and General Relativity predict field coherence under Lorentz invariance. The AxAbsEnt model predicts:

\begin{itemize}
    \item Deviation in gravitational acceleration at submillimeter scales.
    \item EM-field boundary distortions near trans-absolute resonance conditions.
    \item Effective mass anomalies in composite bosonic states beyond energy thresholds.
\end{itemize}

\subsection{Experimental Configurations}

\begin{itemize}
    \item \textbf{CERN LHC}: Configure for vector-boson fusion exceeding 15~TeV and measure asymmetries in decay widths.
    \item \textbf{Eöt-Wash Experiments}: Reconfigure torsion balance to 10–100 micron separation to measure predicted deviation:
    \[
    \Delta a(r) \approx \alpha e^{-\lambda r} \cos(\omega_r r)
    \]
    \item \textbf{Modified Casimir Chamber}: Use dynamic plate spacing under high-frequency control to probe emergent non-EM signatures.
\end{itemize}

\section{Prediction P2: Vacuum Resonance Activation}

\subsection{Prediction Statement}

Vacuum fluctuations are not stochastic but emergent from transfinite mediator chains among absolutes. The theory predicts quantized vacuum resonance signatures at specific modulation thresholds.

\subsection{Experimental Triggers}

\begin{itemize}
    \item High-frequency laser-pumped microcavities (\(> 10^{15} \text{Hz}\)) with QED-vacuum resonance thresholds.
    \item SQUID-based fluctuation detectors configured to read frequency shift noise at cryogenic temperatures.
\end{itemize}

\subsection{Predicted Output}

\[
\delta E_{\text{vac}} \sim \frac{1}{\sqrt{N}} \sum_{k=1}^N \Theta_k(\mathbb{M})
\]
where \(\Theta_k\) are resonance modulators derived from mediator space curvature.

\section{Prediction P3: Cosmological Curvature Deviation}

\subsection{Prediction Statement}

The curvature of space-time is a macroscopic projection of transfinite entropy flux. The theory predicts systematic curvature entropy deviation in regions of high cosmic void density.

\subsection{Observables}

\begin{itemize}
    \item Enhanced lensing anomalies at inter-supercluster scales
    \item Anisotropic residuals in CMB beyond Planck noise floor
    \item Deviations in galaxy redshift alignment from predicted gravitational potential
\end{itemize}

\subsection{Target Experiments}

\begin{itemize}
    \item \textbf{James Webb Space Telescope (JWST)}:
    Search for unaligned lensing anomalies in deep-field mapping.
    \item \textbf{Dark Energy Survey (DES)}:
    Re-analyze baryon acoustic oscillation (BAO) residuals with entropy tensor projection models.
\end{itemize}

\section{Prediction P4: Information Transfer Beyond Entanglement}

\subsection{Prediction Statement}

The model predicts information transfer between non-entangled systems via mediator space resonance alignment, violating Bell locality without violating causality.

\subsection{Test Protocol}

\begin{itemize}
    \item Prepare two isolated superconducting quantum interference systems with independent entangled qubit arrays.
    \item Vary interaction phase gates in one system and detect nonlocal entropy correlation in the other.
\end{itemize}

\subsection{Predicted Violation Signature}

Let \(\rho_A\) and \(\rho_B\) be isolated reduced states:
\[
\Delta H(\rho_B | \rho_A) < \epsilon \quad \text{without causal link or prior entanglement}
\]

This violates conventional quantum postulates, testable via entropy cross-correlation between isolated measurement runs.

\section{Conclusion}

The Enhanced Mathematical Ontology of Absolute Nothingness produces a series of explicit experimental predictions in gravity, quantum vacuum behavior, cosmology, and information dynamics. Each prediction is derived from mathematical operator formalism in AxAbsEnt and can be simulated numerically or verified empirically. Validation or falsification of these claims offers the first fully ontological test of the origin of force and interaction.

\section*{Acknowledgements}
The author acknowledges the development of this framework under the AxAbsEnt execution engine and the Unified Theory Laboratory at RJV Technologies Ltd.

\section*{References}
\vspace{-1em}
\begin{itemize}
    \item R. Do Vale, "Enhanced Mathematical Ontology of Absolute Nothingness", (2025)
    \item A. Einstein, "The Foundation of the General Theory of Relativity", (1916)
    \item S. Weinberg, "The Quantum Theory of Fields", Vol. III
    \item Planck Collaboration, “Planck 2018 Results”, A\&A (2020)
    \item CERN LHC Collaboration Papers, 2012–2024
\end{itemize}

\end{document}
